\chapter*{Acknowledgements}
%\startcontents[chapters]
\addcontentsline{toc}{chapter}{Acknowledgements}  

First and foremost, I would like to express my gratefulness and sincere to my supervisor, engineer Romain Daden, for giving me a wonderful opportunity to work and study in this machine learning topic, for the continuous support during my apprenticeship at SFR-Altice and for his patience, motivation and immense knowledge. His guidance helps me to follow the correct path in the time I worked. I could not have imagined having a better supervisor and mentor in my very last and important year of study to finish the Master's program.

My sincere also goes to my extraordinary team at SFR Analytics, who do not hesitate to help me with anything, even helping me with difficulties in life the very first time I am in France. I will be unable to have such a nice and remarkable apprenticeship without them.

I would like to show my thankfulness to my academic tutor, Kim Nguyen, and to all of my teachers who have been alongside me for two years of my master's at both Université Paris Cité and Université Paris Saclay. It is a great pleasure to be your student.

I would like also to give great respect to the company of Altice SFR, which provide me with a place to work, and the equipment that I use during the apprenticeship, my very kind housemates, as well as my classmate, to help me with the very first day I came to Paris.

Last but not least, I also want to give great gratefulness to my family for giving me a lot of mental as well as financial support. This thesis could not be done without them.



