\chapter{Conclusion}

\startcontents[chapters]
\printmyminitoc{
}

The apprenticeship offers a valuable opportunity for me to improve my skills, and a chance to apply what I have learned over the courses at the university on real projects. Equally significant is the examination of the result at the end of this journey — what the experience has brought to me and, conversely, what I have contributed to the company.

\section{Knowledge acquired after the apprenticeship}

Through the apprenticeship, I've acquired a wealth of valuable knowledge an
d insights. I've honed my skills in data collection, analysis, and interpretation, especially in the context of customer interactions. Additionally, I've applied and learned a lot of things from multiple technologies such as NLP, working with cloud and computer vision. These experiences have not only expanded my technical expertise but have also deepened my understanding of the intricacies of the telecommunications industry and the significance of customer-centric strategies. Not only that, it is also important for me to acquire the necessary soft skills, teamwork skills, and communication skills.

Overall, the apprenticeship has equipped me with a diverse skill set and a practical perspective that I can apply to future endeavors.


\section{Contributions}

In the part of contributions to the company, my role as an apprentice data scientist apprentice at SFR entailed a range of responsibilities. I actively engaged in data collection, analysis, and the application of advanced techniques to extract meaningful insights from complex datasets. This process was necessary in informing strategic decisions, optimizing operational processes, and enhancing customer experiences. Furthermore, my collaborative interactions with cross-functional teams facilitated the alignment of data-driven insights with business objectives and promoted an environment of better decision-making. 

I hope my contribution will help the business for SFR not only resolve current problems and business, but also it could use the research about the cloud in the near future as planned.



